### 2017-05-30 paper.tex
Fix emphasis

Learner profiles have five parts:
the learner's general background,
what they already know,
what *they* think they want to do,
how the material will help them,
and any special needs they might have.
A learner profile for a weekend programming workshop for new college students might be:

@@

Experience shows that even a brief introduction to a handful of key practices
can help collaborative lesson development in at least three ways.
If people have a shared understanding of how lessons should be developed,
it is easier for them to work together.
Less obviously,
if people have a shared model of how lessons are going to be *used*,
they are more likely to try to build the same kind of material.
Finally,
teaching people how to teach is a great way to introduce them to each other and build community.

@@

Pre- and post-class surveys also are essential in focusing in on the audience for a given lesson.
Refering back to Rule~1, it can sometimes be difficult for lesson developers to understand the frame of a given learner
so surveys (particularly post-class surveys) can reveal hidden assumed knowledge
that can be expanded on or acknowledged to refine the target audience.

@@

If there are several complementary ways to explain something,
or several points of views that can cohabit respectfully,
it may be possible to present them side by side.
There are actually good pedagogical reasons to do this even if contributors *don't* disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one (FIXME: cite choral explanations).

>>>>

Learner profiles have five parts:
the learner's general background,
what they already know,
what \emph{they} think they want to do,
how the material will help them,
and any special needs they might have.
A learner profile for a weekend programming workshop for new college students might be:

@@

Experience shows that even a brief introduction to a handful of key practices
can help collaborative lesson development in at least three ways.
If people have a shared understanding of how lessons should be developed,
it is easier for them to work together.
Less obviously,
if people have a shared model of how lessons are going to be \emph{used},
they are more likely to try to build the same kind of material.
Finally,
teaching people how to teach is a great way to introduce them to each other and build community.

@@

Pre- and post-class surveys also are essential in focusing in on the audience for a given lesson.
It can sometimes be difficult for lesson developers to understand the frame of a given learner
so surveys (particularly post-class surveys) can reveal hidden assumed knowledge
that can be expanded on or acknowledged.

@@

If there are several complementary ways to explain something,
or several points of views that can cohabit respectfully,
it may be possible to present them side by side.
There are actually good pedagogical reasons to do this even if contributors \emph{don't} disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one (FIXME: cite choral explanations).
